---
title: "Create the treatment and control group table"
author: "Yunlin Zhou"
date: "2023-03-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```


```{r}
# Import the Amazon Fulfillment Center Coordinates Rounded table
fc_df <- read.csv("amazon_fulfillment_coordinates_rounded.csv") %>%
   rename(lat_rounded_fc = lat_rounded, lng_rounded_fc = lng_rounded)

# Import the RUCC Score 2013 table
rucc_df <- read.csv("us_county_fips_coordinates_rounded.csv") %>% drop_na(RUCC_2013) %>%
  rename(county_fips = FIPS)

```

# Merge the Amazon FC and RUCC score table based on FIPS code into one table

```{r}
# Left join the RUCC Score 2013 table and the Amazon coordinates table
fc_rucc <- left_join(rucc_df, fc_df, by = "county_fips")
row_indices <- order(fc_rucc$RUCC_2013)
fc_rucc <- fc_rucc[row_indices, ]
```

# Subset the merged table based on RUCC score (a list of 9 subset lists)

```{r}
# Create a list to store the subsets
rucc_score_subsets <- list()

# Loop through each unique RUCC_2013 value
for (i in unique(fc_rucc$RUCC_2013)) {
  
  # Subset the table to only include rows with the current RUCC_2013 value
  subset_table <- fc_rucc[fc_rucc$RUCC_2013 == i, ]
  
  # Add the subset table to the list of subsets
  rucc_score_subsets[[i]] <- subset_table
  
}

```

# Extract the 9 subsets from the list

```{r}
# Loop through each unique RUCC score value
for (i in unique(fc_rucc$RUCC_2013)) {
  
  # Extract the subset table for the current RUCC score value
  table_name <- paste0("rucc_score", i )
  assign(table_name, as.data.frame(rucc_score_subsets[[i]]))
}

```

# Check the number of Amazon fulfillment centers with diffrent Rucc socre

```{r}
# Create a list of data frames
df_list <- list(rucc_score1, rucc_score2, rucc_score3, rucc_score4, rucc_score5, rucc_score6, rucc_score7, rucc_score8, rucc_score9)

# Loop over each data frame and check the address column for missing values
for (i in 1:9) {
  
  # Check if the specified column is null
  if (all(is.na(df_list[[i]]$address))) {
    print(paste("There are no Amazon fulfillment centers in  the area where the Rucc socre equals", i, "."))
  } 
  
  else {
    print(paste("There are Amazon fulfillment centers in the area where the Rucc socre equals", i, "."))
    
  # Count the number of non-null rows in "my_column"
    non_null_rows <- sum(!is.na(df_list[[i]]$address))

  # Print the result
    print(paste("The number of Amazon fulfillment centers where the Rucc socre equals", i, "is", non_null_rows))
  }
}

```

Since the only Amazon fulfillment center where the Rucc socre equals 7 opened in year 1999, we will exclude this Amazon fulfillment center.

#	Subset to fulfillment centers that opened 2005-2017 (rucc_score1_combined; rucc_score2_combined; rucc_score3_combined; rucc_score4_combined)

```{r}
# create a list of the table names
table_names <- c("rucc_score1", "rucc_score2", "rucc_score3", "rucc_score4")

# loop through each table and apply the code
for (name in table_names) {
  # get the table object by name
  table <- get(name)
  
  # filter the table to include only years 2005-2017 and add a treatment/control column
  treatment <- table %>%
    filter(year_opened %in% (2005:2017)) %>%
    mutate(group = "treatment")
  
  control <- table %>%
    filter(is.na(address)) %>%
    mutate(group = "control")
  
  # vertically combine the treatment and control groups into a new table
  combined_table <- rbind(treatment, control)
  
  # assign the new table to a new object
  new_name <- paste0(name, "_combined")
  assign(new_name, combined_table)
}

```

### Combine the 4 subsets into a new table

```{r}
# Combine the subsets into a new table

fc_rucc_combined_full <- rbind(rucc_score1_combined, rucc_score2_combined, rucc_score3_combined, rucc_score4_combined)

fc_rucc_combined <- fc_rucc_combined_full %>%
  select(group, county_fips, State, County_Name, RUCC_2013, lat_rounded, lng_rounded, oc_formatted, lat_rounded_fc, lng_rounded_fc)

write.csv(fc_rucc_combined_full, "fc_rucc_combined_full.csv", row.names = FALSE)

write.csv(fc_rucc_combined, "fc_rucc_combined.csv", row.names = FALSE)
```

